---
title: "Homework: Reviewing R and Python"
execute:
  error: true
author: "Your Name"
output: html_document
---


A palindrome is a string that is equal to the reverse of that string, such as "Mom", "Hannah" or "We panic in a pew."

Traditionally, a phrase is tested for being a palindrome once all spaces and punctuation has been removed, and all letters are written in the same case. You will need to think about how to do these tasks in R and python.

# Problem 1: Simple Palindromes
## Pseudocode

Write a detailed list of steps to process a string named `test` to test that it is a palindrome. 

You may find it helpful to write down some test words and work through them as if you were an algorithm. If you do this, please take a picture of your scratch paper, put it in the homework directory, and add it to your git repository along with your assignment solution.

Hint: The final items in this list of steps should be defining a variable `revtest` that is `test` with the letters reversed, and then comparing `test` and `revtest` for equality.



## R

Turn your pseudocode into a sequence of statements in R that work with a variable named `test`.
At this point, there is no need to write these steps in a function - we'll get there.

```{r}
test <- "Hannah"
test2 <- "not-a-palindrome"

# Your steps go here
```


## Python

Turn your pseudocode into a sequence of statements in python that work with a variable named `test`.
At this point, there is no need to write these steps in a function - we'll get there.

```{python}
test = "Hannah"
test2 = "not-a-palindrome"

# Your steps go here
```


# Problem 2: Functional Palindromes

In R and Python, use your code above to create a function, `palindrome`, which takes an argument, `x`, and returns a logical value indicating whether `x` is a palindrome.

```{r}
# Your R function goes here
```

```{python}
# Your python function goes here
```


# Problem 3: Vectors of Palindromes

Use a loop, map, or apply statement to find all of the palindromes in a vector. I should be able to provide a different vector and use your function to find all of the palindromes.

```{r}
test_vec <- c("taco cat", "UFO tofu", "In palindromes, spacing, punctuation, and capitalization are usually ignored.", "Borrow or rob?", "dithyrambic", "Never odd or even.", "R rules, Python drools!", "Won't lovers revolt now?", "Ma is a nun, as I am.")

```


```{python}
test_vec = ["taco cat", "UFO tofu", "In palindromes, spacing, punctuation, and capitalization are usually ignored.", "Borrow or rob?", "dithyrambic", "Never odd or even.", "R rules, Python drools!", "Won't lovers revolt now?", "Ma is a nun, as I am."]
```
